### 2013-07-02 inst/examples/sensitivity.Rmd
example GP sensitivity results

  X = c(rep(0,nz), pmax(rep(0,Tobs-1), x[1:(Tobs-1)]))
  Y = c(rep(0,nz), x[2:Tobs]))

@@

  Profit <- sims_data[, sum(profit), by=c("reps", "method")]
  tmp <- dcast(Profit, reps ~ method)
  tmp <- tmp / tmp[,"True"]
  tmp <- melt(tmp[2:dim(tmp)[2]])
  actual_over_optimal$GP

@@

```{r}
yields
#yields <- melt(yields, id=c("method", "V1", "sd"))
#ggplot(yields) + geom_histogram(aes(V1)) + facet_wrap(~method, scale='free')
````

>>>>

  X = c(rep(0,nz), pmax(rep(0,Tobs-1), x[1:(Tobs-1)]))
  Y = c(rep(0,nz), x[2:Tobs])

@@

  Profit <- sims_data[, sum(profit), by=c("reps", "method")]
  tmp <- dcast(Profit, reps ~ method)
  tmp <- tmp / tmp[,"True"]
  tmp <- melt(tmp[2:dim(tmp)[2]])
  tmp$value[tmp$variable == "GP"]

@@

```{r}
yields_dat <- melt(yields)
names(yields_dat) <- c("replicate", "simulation", "value")
#class(yields_dat$simulation) = "factor"

col_metadata <- c(replicate = "id of individual replicates using identical settings, relative to the theoretical optimum",
  simulation = "id number for the simulation, which varies the simulated data used",
  value = "total profit achieved by specified run")
unit_metadata <- list(replicate = list(1:dim(yields)[1]), simulation = list(1:dim(yields)[2]), value = "currency (arbitrary)")
```

```{r}
ggplot(yields_dat) + geom_density(aes(value)) 
````

```{r}
ggplot(yields_dat) + geom_density(aes(value, group=simulation)) 
````

```{r}
ggplot(yields_dat) + geom_density(aes(value, group=replicate)) 
````
